A Fredholm integral equation approach to computing Stokes eigenvalues in the plane

### 2019-03-13 doc/draft-01-stokes/03analysis2.tex

>>>>

In practice, using the Kress-quadrature for large problems is problematic owing to the global
nature of the quadrature rule. 
The coupling with fast direct solvers for computing determinants also results in $O(N^2 \log{N})$ 
determinant evaluation since evaluating each matrix entry costs $O(N)$, where 
$N$ is the number of discretization points on the boundary.
Over the last two decades, many high-order quadrature methods which are compatible with
fast algorithms like the fast multipole method (and fast direct solvers as well, 
since each matrix entry requires O(1) work) have been developed for solving
integral equations.
Extensive numerical evidence suggests that the zeros of the 
determinants of linear systems discretized using 
these quadrature methods are also high order approximations of Dirichlet eigenvalues
for the Stokes PDE--- the error is observed to be proportional to the quadrature error
for the eigenfunction $\bt^{-}$ associated with the eigenvalue.
We leave a proof of this to future work.
